Confirmation of \srcfull{} as a long period radio transient

### 2025-04-25 paper/main.tex
Updated paper from Overleaf

@@

\begin{deluxetable*}{cccccc}
\tablecaption{Observations}
\tablehead{
\colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\
\colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
}
\startdata
59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
60092 - 60093 & MeerKAT & & & & 4 \\
60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 18 \\
60503 & ASKAP &  & 887.5 & 288 & 1 \\
60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 16 \\
60602 & MeerKAT & & 812.8 & 495.3 & 1 \\
\enddata
\tablenotetext{a}{Original discovery \citep{2024MNRAS.535..909D}}
\end{deluxetable*}

@@

All observed pulses consist of a single burst, approximately Gaussian in shape, with the sole exception of the MeerKAT pulse observed on 2024-10-19, for which two bursts were observed separated by ${\sim}125\,$s.
Generally, the MWA pulses tend
\begin{itemize}
    \item to be wider than their higher frequency counterparts,
    \item to exhibit an asymmetry similar to scattering, and
    \item to be very similar in morphology to each other.
\end{itemize}

The asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1 GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming a DM of 710\,pc\,cm$^{-3}$.
The effect of scattering on the timing is discussed in \S\ref{sec:timing} below.

@@

@@

\subsection{Scattering}

\begin{figure*}[pt]
    \centering
    \includegraphics[width=0.9\linewidth]{pulsestack.pdf}
    \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris. The dashed red vertical line marks zero phase. Baselines have been fitted and subtracted from each lightcurve.}
    \label{fig:pulsestack}
\end{figure*}

@@

>>>>

\DeclareMathOperator{\erfcx}{erfcx}

@@

\begin{deluxetable*}{cccccc}
  \tablecaption{Observations}
  \tablehead{
    \colhead{Date range} & \colhead{Telescope} & Project & \colhead{$\nu$} & \colhead{$\Delta\nu$} & \colhead{Number of} \\ 
    \colhead{(MJD)} & & & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{pulses}
  } 
  \startdata
  59965 & ASKAP\tablenotemark{a} & SB47253 & 887.5 & 288 & 1 \\
  59966 & MWA & G0060 & 161.92 & 15.36 & 1 \\
  %60084 & MWA & G0057 & 154.24 & 30.72 & $\le$ 1 \\
  60092 - 60093 & MeerKAT & & & & 4 \\
  60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & 18 \\
  60503 & ASKAP &  & 887.5 & 288 & 1 \\
  60572 & MWA & D0042 & 184.96 & 30.72 & 4 \\
  60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & 16 \\
  60602 & MeerKAT & & 812.8 & 495.3 & 1 \\
  \enddata
  \tablenotetext{a}{Original discovery \citep{2024MNRAS.535..909D}}
\end{deluxetable*}

@@

All observed pulses consist of a single burst, approximately Gaussian in shape, with the sole exception of the MeerKAT pulse observed on 2024-10-19, for which two bursts were observed separated by ${\sim}125\,$s.
Generally, the low-frequency (MWA) pulses tend
\begin{itemize}
        \item to be wider than their higher frequency counterparts,
              \item to exhibit an asymmetry similar to scattering, and
                    \item to have minimal pulse-to-pulse variation.
\end{itemize}

The low-frequency asymmetry is consistent with a scattering time scale of a few tens of seconds at MWA frequencies, which scales to a few tens of milliseconds at 1\,GHz.
This is in broad agreement with the model predictions of NE2001 ($\tau_{\rm sc,1GHz} = 0.066\,$s) and YMW16 ($\tau_{\rm sc,1 GHz} = 0.075\,$s) at the source's location assuming a DM of 710\,pc\,cm$^{-3}$.

To account for the asymmetry, we fit exponentially modified Gaussians to each pulse with the form,
\begin{equation}
  \begin{aligned}
        y(t) &= A \frac{\sigma}{\tau}\sqrt{\frac{\pi}{2}}
                   \exp\left(-\frac12 \left( \frac{t - \mu}{\tau} \right)^2 \right) \\
                            &\qquad \erfcx \left(\frac{1}{\sqrt{2}} \left(\frac{\sigma}{\tau} 
                             - \frac{t - \mu}{\tau} \right) \right),
  \end{aligned}
  \label{eqn:emg}
\end{equation}
where $A$, $\mu$, and $\sigma$ are the height, location, and scale of an unscattered Gaussian pulse, and the scattering time scale was fixed at
\begin{equation}
      \tau = 0.07\, \left(\frac{\nu}{\rm GHz}\right)^{-4} \, {\rm s},
\end{equation}
according to each observation's centre frequency.
A pulse stack containing all observed pulses and their fits is shown in Fig. \ref{fig:pulsestack}.

\begin{figure*}[tp]
      \centering
          \includegraphics[width=0.9\linewidth]{pulsestack.pdf}
              \caption{Pulsestack of barycentred, dedispersed profiles from the ephemeris. The dashed red vertical line marks zero phase. Baselines have been fitted and subtracted from each lightcurve. The blue dashed lines show (normalised) fitted Gaussians without scattering (see main text for details).}
                  \label{fig:pulsestack}
\end{figure*}

For the MeerKAT pulse with two components, we fit only the brighter component.

@@

Because the large scattering time scale at low frequencies significantly distorts the pulse shapes, we identified the times of arrival (ToAs) with the fitted $\mu$ parameter in the fits given in Eq. \eqref{eqn:emg}, which represents the location of the Gaussian pulse before scattering.

The distortion of the pulse shapes at MWA frequencies creates a degeneracy between DM and scattering time scales that is not easily disambiguated.
This is demonstrated in Fig. \ref{fig:stacked_spectra}, which shows stacked MWA and MeerKAT spectra.
Without accounting for scattering, the measured DM would significantly exceed the 710\,pc\,cm$^{-3}$ (cyan lines).
The scattering predicted by Galactic electron density models, however, is sufficient to account for the apparent extra delay.

The degeneracy between DM and scattering (as well as variations in pulse width and ToA) render the lower frequency pulses less useful for measuring either DM or scattering alone.
Breaking the degeneracy is possible in principle with a much higher S/N average profile than what is possible with the current data set.

For this work, we therefore did not attempt to fit the DM or the scattering time scale individually.
Instead, we adopted the original ASKAP measurement of ${\rm DM} = 710\,$pc\,cm$^{-3}$ and a scattering timescale of $\tau_{\rm sc,1 GHz} = 0.07\,$s for the timing analysis.
We did, however, confirm that fits to individual pulses using Eq. \eqref{eqn:emg}, but also allowing the $\tau$ parameter to freely vary, produced fitted values that were broadly consistent with our chosen value.

The ToAs were then fit

@@

@@

The precursor burst seen with MeerKAT is apparently unique, and is not visible at other telescopes and frequencies, even after averaging them together to make a single profile.
The only burst of comparable S/N, and at a similar frequency, in which the dimmer precursor component might be expected to be visible is the original 2023-01-21 ASKAP burst \citep{2024MNRAS.535..909D}, where again it is absent.

The two pulses observed in January 2023 (the original ASKAP pulse and the MWA (IPS) pulse observed the following day) are significantly wider than all other pulses, suggesting that a morphological change occurred between
